---
title: "Setup R modules"
author: "hongc2@ccf.org"
date: "1/16/2020"
output:
  html_document:
    df_print: paged
objectives: Download 10x PBMC data for input; Install R modules required
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## To install R
- Install R 3.5.3+ (Note that we have tested R scripts in the session with R3.5.3)
- Open an internet browser
- For Windows user: Download [R3.5.3](http://healthstat.snu.ac.kr/CRAN/bin/windows/base/old/3.5.3/R-3.5.3-win.exe) or [R3.6.2](http://healthstat.snu.ac.kr/CRAN/bin/windows/base/old/3.6.2/R-3.6.2-win.exe)
- Click "Download R for Windows" and save the executable file somewhere on your computer.  Run the .exe file and follow the installation instructions.
- For MacOSX user: Download [R3.6.2](https://cran.seoul.go.kr/bin/macosx/R-3.6.2.pkg)
- Now that R is installed, you need to download and install RStudio.

## To install Rstudio
- Go to [rstudio](www.rstudio.com) and click on the "Download RStudio" button.
- Click on "Download RStudio Desktop."
- Click on the version recommended for your system, or the latest Windows version, and save the executable file.  Run the .exe file and follow the installation instructions. 

## To install R modules to accomplish the experiments in the tutorial
- Launch Rstudio
- Install the following R library modules,
```{r r_module_setup, echo=TRUE, eval=TRUE}
tutorial_pkgs <- c('multtest','R.utils','Seurat','data.table','openxlsx','reshape2','dplyr','reticulate','cowplot','grid','gridExtra','ggplot2','randomcoloR','pheatmap','stringr','tools')

for (pkg in tutorial_pkgs) {
  if( !is.element(pkg, .packages(all.available = TRUE)) ) {
    message(sprintf("installing %s ...",pkg))
    install.packages(pkgs=pkg)
    message("Done.")
  }
  message(sprintf("loading %s ...",pkg))
  library(pkg,character.only = TRUE)
}
```